Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-07 paper/ms.tex
update ms (ADU sugggestions)
Co-authored-by: Alexandre David-Uraz <adu@udel.edu>

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit sharp and
  periodic optical light curves.  Previous studies have indicated that
  these stars are typically disk-free pre-main-sequence M dwarfs with
  rotation periods ranging from 0.2 to 2 days.  To advance our
  understanding of these enigmatic objects, we conducted a blind
  search using TESS 2-minute data of \nstarssearched\ K and M dwarfs
  with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\ high-quality
  CPVs, and subsequently determined that most are members
  of stellar associations.  Among the new discoveries are the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
  12-502, exhibited up to eight flux dips per cycle. Some of these
  dips coexisted with slightly different periods, and the
  shortest-duration LP 12-502 dips precisely matched the expected
  timescale for transiting small bodies at the corotation radius.
  Broadly, our search confirms that CPVs are mostly young
  ($\lesssim$150\,Myr) and low-mass ($\lesssim$0.4\,$M_\odot$).  The
  flux dips characteristic of the class have lifetimes of $\approx$100
  cycles, although stellar flares seem to induce sudden dip collapse
  once every few months.  The most plausible explanation for these
  phenomena remains corotating concentrations of gas or dust.  The gas
  or dust is probably entrained by the star's magnetic field, and the
  sharp features could result from a multipolar field topology, a
  hypothesis supported by correspondences between the light curves of
  CPVs and of B stars known to have multipolar magnetic fields.
  %
\end{abstract}

@@

The dust clump and gas prominence hypotheses are conceptually
similar; one could imagine dust or gas accumulating in
either of the geometries shown in Figure~\ref{fig:f1}.  The main
distinguishing factor between the two models is the composition of the
occulting material.   ``Dust clumps'' invoke opacity from dust, which
would need to be collisionally charged \citep{2023MNRAS.518.4734S}.
``Gas prominences'' invoke opacity from partially-ionized gas, likely
bound-free transitions in hydrogen or perhaps a molecular opacity.
Unambiguous evidence in support of either scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

@@

We homogeneously assessed whether the objects identified using the
dip-counting (Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) approaches were consistent with
expectations for CPVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise
    oddly-shaped dips.
  %
  \item Dip phases mostly repeat over $\approx$30\,day sector duration.
\end{itemize}
\vspace{-2pt}
We also noted ''possible'' CPVs for which the classification was more
ambiguous, and ``false positives'' that are definitely not CPVs.  The
most common false positives for both the Fourier and dip-counting
techniques were eclipsing binaries, ordinary spotted rapid rotators,
and light curves that were complex due to multiple stars contributing to the
photometric aperture.  Our specialized dip-counting pipeline flagged
\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
subsequently labeled either good or possible CPVs.  From the more
general Fourier pipeline, $\approx$0.5\% of stars that passed the
12-$\sigma$ peak threshold were eventually classified as CPVs.

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

@@

{\it Multiple periodic TESS signals}---During our visual analysis of
the TESS light curves and PDM periodograms, we flagged sources with
beating light curves, and with PDM periodograms that showed multiple
periods.  We also attempted to disentangle the two signals by
subtracting the mean CPV signal over each sector, and then repeating
the phase-dispersion minimization analysis.  The results of this effort
are summarized in the secondary periods, $P_{\rm sec}$, listed in
Table~\ref{tab:thetable}, which we required to be at least 5\%
different from the primary period.  This process yielded
\ngoodmultperiodflag/\ngoods\ high-quality CPVs with secondary
periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous sample met
the same criterion.  Of the \ngoodhighruwe\ good CPVs with ${\rm
RUWE}_{\rm DR3}> 2$, \ngoodruweandmultperiod\ also showed secondary
periods in the TESS light curves.  Considering the weaker threshold of
${\rm RUWE}_{\rm DR3}> 1.4$,
\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs showed secondary
TESS periods.

@@

Both of the stars with IR exceses are in the TW Hydrae association
($\approx$10\,Myr).  They have periods of 38\,hr and 44\,hr,
respectively.  In our initial labeling, we labeled both as
``ambiguous'' CPVs because the dips in their Sector~36 light curves
seemed to stochastically evolve over only one or a few cycles, which
is atypical for CPVs; their periods were also long in comparison with
most of the other CPVs.  Inspection of additional sectors clarified
that both sources are dippers, not CPVs (see the online plots in
Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve of
shows completely different behavior from Sector~36, with variability
amplitudes of $\pm 50\%$ and no obvious periodicity.  TIC~57830249
also shows continuum emission at 1.3\,mm \citep{2015A&A...582L...5R},
which suggests that cold dust grains are present.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f5.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CPVs identified by our search}.
      CPVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CPVs in
      Table~\ref{tab:thetable} are the dark blue circles; \nmaybes\
      ambiguous CPV candidates are light blue circles.  Unresolved
      binaries (red circles) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 2-minute cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CPVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CPV periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

A significant fraction of the CPVs show indications of unresolved
binarity.  Excess noise above the Gaia single-source astrometric model
is common (\ngoodhighruwe/\ngoods\ high-quality CPVs have RUWE$_{\rm
DR3}$$>$2), as is the presence of multiple periods in the TESS light
curves (\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise
almost always implies multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CPVs).  The
latter observation corroborates the claim that most sources with
RUWE$_{\rm DR3}$$>$2 are binaries with projected apparent separations
below 1$''$, and projected physical separations $\lesssim$50\,AU.
These observations are also in agreement with previous analyses of
multi-periodic low-mass discovered by K2, which found that such
systems are almost always binaries
\citep{2018AJ....156..138T,2018AJ....156..275S}.

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CPVs
for which TESS 2-minute cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
confirmed \ngoods\ CPVs in our catalog; for plotting purposes we show
the brightest 27.  
We have defined $\phi=0$ for each sector to be the time of minimum
light observed in that sector, rather than using a consistent phase
definition across multiple sectors.
This is because for most of the sources we do not know the period at the
precision necessary to be able to accurately propagate an ephemeris
over two years.  The achievable period precision, $\sigma_P$, can be
estimated as
\begin{equation}
  \sigma_{P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
  \label{eq:periodprecision}
\end{equation}
for $N_{\rm baseline}$ the number of cycles in the observed baseline
and $\sigma_{\phi}$ the phase precision with which any one feature
(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day baseline
over a single TESS sector yields
$\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the
population shown in Figure~\ref{fig:evoln}; propagated forward 1{,}000
cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
Measuring the period independently for each sector did not reveal
evidence for significant ($>$3$\sigma$) changes in period, implying
a period stability of $\lesssim$0.1\% over two years.

@@

The behavior during Sectors 53--58 (cycles 1233-1481) is comparatively tame; the light curve shows
only four to six dips per cycle.  Some dips remain stable in depth and
duration over this five-month interval.  Other dips grow, like the one
at $\phi = +0.06$ between cycles 1499 and 1481.  Other dips, such as
the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
The most dramatic state change occurs during cycle 1241, when a large
dip switches from a depth of 3\% and a duration of 3 hours to a depth
of 0.3\% and a duration of 1 hour.

@@

Examining Figure~\ref{fig:cqvs}, it is clear that CPV dips can be
asymmetric but it is not obvious whether there is a preference for
sharper ingresses or sharper egresses.  In some cases (e.g.
TIC~425933644), the flux variations do not resemble isolated dips,
making the meaning of ``ingress'' and ``egress'' unclear.  In other
cases, such as Sector~36 of TIC~89463560, there is a sharp drop with
an exponential return to the baseline flux, resembling the signatures
of exocomet \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
and the outflowing exospheres of some transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

@@

\citet{2017AJ....153..152S} previously noted a possible connection
between the CPVs and rapidly rotating magnetic B stars such as
$\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
corotation \citep{2005ApJ...630L..81T}.  The $\sigma$~Ori class is
distinct from Be-star decretion disks, which do not have any obvious
connection to the stellar magnetic field \citep{2013A&ARv..21...69R}.

@@

Two interesting and possibly telling exceptions to the rule that
magnetic B stars have simple light curves are HD~37776 and HD~64740.
HD~37776 is known from spectropolarimetry to have an extreme field
geometry dominated by high order multipoles
\citep{2011ApJ...726...24K}.  The field geometry of HD~64740, while
potentially less extreme, is also less well-studied
\citep[see][Ch.~4]{1988PhDT........53B}.  Recent TESS light curves
of these two B stars appear surprisingly similar to the CPV light
curves \citep{2020pase.conf...46M}.  The middle row of
Figure~\ref{fig:bstar} shows the phased TESS light curves for these
two stars, with by-eye best-matching CPVs shown underneath for
comparison.  The number of dips per cycle, the shapes of the dips, and
the dip depths relative to the sinusoidal envelope are all similar.
This connection suggests that the highly structured light curves of
both the M dwarfs and the B stars are associated with (and perhaps
caused by) strong non-dipolar magnetic fields.  Non-dipolar fields for
M dwarfs are plausible, given that Zeeman Doppler Imaging has revealed
non-axisymmetric magnetic field patterns for the few M dwarfs for
which this technique is technically feasible \citep[see][and
references therein]{2021A&ARv..29....1K}.

The physical similarity between the B stars and the M dwarfs
presumably has its origin in the existence of a ``centrifugal
magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.  In other words,
both classes of objects probably satisfy the condition $R_{\rm m} >
R_{\rm c}$, for $R_{\rm m}$ the magnetosphere radius (sometimes called
the Alfv\'en radius).  Provided that charged particles are confined to
move along magnetic field lines, stable points that balance the
centrifugal force and gravity can then exist at the corotation radius
\citep[e.g.][]{2005MNRAS.357..251T}.  In the converse ``dynamical''
case, when $R_{\rm m} < R_{\rm c}$, material interior to the
magnetospheric radius returns to the stellar surface over the
free-fall timescale.  A simple estimate assuming a dipole field with
$B_0\approx1\,{\rm kG}$ at the star's surface, a local plasma number
density $n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature
$10^6\,{\rm K}$ gives magnetospheric radii of order a few times the
corotation radii, $R_{\rm c}$.  This suggests that the existence of a
centrifugal magnetosphere is plausible for young, rapidly rotating M
dwarfs.

@@

@@

@@

    \item The CPV peaks and dips evolve over timescales that are both secular
      ($\approx$100\,cycles) and impulsive ($<$1 cycle).  Dip growth seems
      to happen over durations of at least ten cycles, and slow dip
      decay can also occur.  ``State-switches'' correspond to dips 
      collapsing instantaneously, and
      occur once every few months for
      both LP~12-502 and TIC~300651846.
      They are almost always linked with
      observed optical flares.  Such switches are suggestive of
      magnetic reconnection opening the ``magnetic cage'' that traps
      the dust.

@@

On the theoretical front, building a physical understanding what sets
the characteristic size scale of the clumping material would help
clarify why the light curves have the bizarre shapes that are
observed.  The relevant puzzles in plasma physics and radiative
transfer could perhaps be connected to our understanding of the
close-in rocky planets that are expected to be present around most of
these stars.

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship, and for helpful conversations with
J.~Spake, A.~Mann, G.~Laughlin, and B.~Draine.  
We are also grateful for the assistance of S.~Yee,
L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and reducing the
HIRES spectra.
This paper relied primarily on data collected by the TESS mission; the specific
2-minute cadence observations can be accessed via
DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
Funding for the TESS mission is provided by NASA’s Science Mission
Directorate.  
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, and J.~Jenkins) and the many TESS team members for their efforts to make the mission a continued success. 
LP 12-502 in particular was observed at 2-minute
cadence thanks to the TESS Guest Investigator programs G022252 (PI:
J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
Sector 53).

>>>>

% 250 word max!
\begin{abstract}
  %
  Complex periodic variables (CPVs) are stars that exhibit sharp and
  periodic optical light curves.  Previous studies have indicated that
  these stars are typically disk-free pre-main-sequence M dwarfs with
  rotation periods ranging from 0.2 to 2 days.  To advance our
  understanding of these enigmatic objects, we conducted a blind
  search using TESS 2-minute data of \nstarssearched\ K and M dwarfs
  with $T$$<$16 and $d$$<$150\,pc.  We found \ngoods\ high-quality
  CPVs, and subsequently determined that most are members
  of stellar associations.  Among the new discoveries are the
  brightest ($T$$\approx$9.5), closest ($d$$\approx$20\,pc), and
  oldest ($\approx$200\,Myr) CPVs known.  One exceptional object, LP
  12-502, exhibited up to eight flux dips per cycle. Some of these
  dips coexisted with slightly different periods, and the
  shortest-duration LP 12-502 dips precisely matched the expected
  timescale for transiting small bodies at the corotation radius.
  Broadly, our search confirms that CPVs are mostly young
  ($\lesssim$150\,Myr) and low-mass ($\lesssim$0.4\,$M_\odot$).  The
  flux dips characteristic of the class have lifetimes of $\approx$100
  cycles, although stellar flares seem to induce sudden dip collapse
  once every few months.  The most plausible explanation for these
  phenomena remains corotating concentrations of gas or dust.  The gas
  or dust is probably entrained by the star's magnetic field, and the
  sharp features could result from a multipolar field topology, a
  hypothesis supported by correspondences between the light curves of
  CPVs and of rapidly-rotating B stars known to have multipolar magnetic fields.
  %
\end{abstract}

@@

While the dust clump and gas prominence hypotheses both invoke
magnetically-entrained material, the two pictures differ in the origin
and the composition of the occulting material.   ``Dust clumps''
invoke opacity from dust, which would need to be collisionally charged
\citep{2023MNRAS.518.4734S}; such dust might be sourced from a
low-mass debris disk.  ``Gas prominences'' invoke opacity from
partially-ionized gas, perhaps bound-free transitions in hydrogen or a
molecular opacity.  The gas might be sourced from a stellar wind.
Unambiguous evidence in support of either scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695
\citep{2016ApJ...830...15J}.

@@

We homogeneously assessed whether the objects identified using the
dip-counting (Section~\ref{subsec:counting}) and Fourier
(Section~\ref{subsec:fourier}) approaches were consistent with
expectations for CPVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CPV if it met
all of the following criteria for at least one TESS sector:
\vspace{-2pt}
\begin{itemize}[leftmargin=*]
  \setlength\itemsep{-2pt}
  \item $P<2$\,days.
  %
  \item At least three dips per cycle, or else otherwise
    oddly-shaped dips relative to expectations for quasi-sinusoidal
    starspot-induced modulation.
  %
  \item Persistent dips over multiple consecutive rotation cycles.
\end{itemize}
\vspace{-2pt}
We also noted ''possible'' CPVs for which the classification was more
ambiguous, and ``false positives'' that are definitely not CPVs.  The
most common false positives for both the Fourier and dip-counting
techniques were eclipsing binaries, ordinary spotted rapid rotators,
and light curves that were complex due to multiple stars contributing to the
photometric aperture.  Our specialized dip-counting pipeline flagged
\nuniqdipflagged\ unique stars for visual inspection; about 20\% were
subsequently labeled either good or possible CPVs.  From the more
general Fourier pipeline, $\approx$0.5\% of stars that passed the
12-$\sigma$ peak threshold were eventually classified as CPVs.

@@

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a truncated normal
distribution with mean $\mu$, standard deviation $\sigma$, and lower
and upper bounds $a$ and $b$.  We validated our chosen upper bound on
$A_{\rm V}$ using a 2MASS color-color diagram.  Finally, using
\texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we sampled
the posterior probability assuming the default Gaussian likelihood,
and set a stopping threshold of ${\rm d}\log \mathcal{Z} < 0.01$,
where $\mathcal{Z}$ denotes the evidence.

@@

{\it Multiple periodic TESS signals}---During our visual analysis of
the TESS light curves and PDM periodograms, we flagged sources with
beating light curves, and with PDM periodograms that showed multiple
periods.  In such cases, we attempted to disentangle the two signals
by subtracting the mean CPV signal over each sector, and we then
repeated the phase-dispersion minimization analysis.  The resulting
secondary periods, $P_{\rm sec}$, are listed in
Table~\ref{tab:thetable}; we required these to be at least 5\%
different from the primary period, and for the majority of secondary
signals the morphologies corresponded to starspot modulation.  This
process yielded \ngoodmultperiodflag/\ngoods\ high-quality CPVs with
secondary periods; \nmaybemultperiodflag/\nmaybes\ of the ambiguous
sample met the same criterion.  Of the \ngoodhighruwe\ good CPVs with
${\rm RUWE}_{\rm DR3}> 2$, \ngoodruweandmultperiod\ also showed
secondary periods in the TESS light curves.  Considering the weaker
threshold of ${\rm RUWE}_{\rm DR3}> 1.4$,
\ngoodweakruweandmultperiod/\ngoodweakruwe\ such CPVs showed secondary
TESS periods.  These results broadly suggest that the secondary
periods are associated with physically-bound binary companions.

@@

Both of the stars with IR excesses are in the TW Hydrae association
($\approx$10\,Myr).  They have periods of 38\,hr and 44\,hr,
respectively.  In our initial labeling, we labeled both as
``ambiguous'' CPVs because the dips in their Sector~36 light curves
seemed to stochastically evolve over only one or a few cycles, which
is atypical for CPVs; their periods were also long in comparison with
most of the other CPVs.  Inspection of additional sectors clarified
that both sources are dippers, not CPVs (see the online plots in
Figure~\ref{fig:vet}).  For TIC~57830249, the Sector~10 light curve 
shows completely different behavior from Sector~36, with variability
amplitudes of $\pm 50\%$ and no obvious periodicity.  TIC~57830249
also shows continuum emission at 1.3\,mm \citep{2015A&A...582L...5R},
which suggests that cold dust grains are present.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.95\textwidth]{f5.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf Properties of CPVs identified by our search}.
      CPVs are mostly pre-main-sequence M dwarfs, younger than
      $\approx$150 Myr, with rotation periods faster than
      $\approx$1\,day.  The \ngoods\ bona fide CPVs in
      Table~\ref{tab:thetable} are the dark blue dots; \nmaybes\
      ambiguous CPV candidates are light blue dots.  Unresolved
      binaries (red rings) are objects for which the Gaia DR3 radial velocity
      scatter exceeded 20\,\kms, or if Gaia ${\rm RUWE}_{\rm DR3}$$>$2
      and multiple photometric signals were present in the TESS light
      curve.  The top panels show the \nstarssearched\ target stars
      with 2-minute cadence TESS data as the shaded gray background;
      darker regions correspond to a larger relative number of
      searched stars.  The lower-left panel compares the
      rotation--color distribution of CPVs against the rotation
      periods of K and M dwarfs in the Pleiades from
      \citet{2016AJ....152..114R}.  The lower-middle panel plots the
      derived corotation radii $R_{\rm c} = (GM/\Omega^2)^{1/3}$ in
      units of stellar radii against the measured CPV periods, in
      units of hours.  Ages in the final panel are known from cluster
			membership.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

A significant fraction of the CPVs show indications of unresolved
binarity.  Excess noise above the Gaia single-source astrometric model
is common (\ngoodhighruwe/\ngoods\ high-quality CPVs have RUWE$_{\rm
DR3}$$>$2), as is the presence of multiple periods in the TESS light
curves (\ngoodmultperiodflag/\ngoods).  Elevated astrometric noise
almost always implies multiple detectable TESS periods
(\ngoodruweandmultperiod/\ngoodhighruwe\ high-quality CPVs).  The
latter observation corroborates the claim that most sources with
RUWE$_{\rm DR3}$$>$2 are binaries with projected apparent separations
below 1$''$, and projected physical separations $\lesssim$50\,AU.
These observations are also in agreement with previous analyses of
multi-periodic low-mass objects discovered by K2, which found that such
systems are almost always binaries
\citep{2018AJ....156..138T,2018AJ....156..275S}.

@@

Figure~\ref{fig:evoln} shows ``before'' and ``after'' views of 27 CPVs
for which TESS 2-minute cadence observations were available at least
two years apart.  Such a baseline was available for 32 of the
\ngoods\ confirmed CPVs in our catalog; for plotting purposes we show
the brightest 27.  
We have defined $\phi=0$ for each sector to be the time of minimum
light observed in that sector, rather than using a consistent phase
definition across multiple sectors.
This is because for most of the sources we do not know the period at the
precision necessary to be able to accurately propagate an ephemeris
over two years.  The achievable period precision, $\sigma_P$, can be
estimated as
\begin{equation}
  \sigma_{P} = \frac { \sigma_{\phi} P } { N_{\rm baseline} },
  \label{eq:periodprecision}
\end{equation}
for $N_{\rm baseline}$ the number of cycles in the observed baseline
and $\sigma_{\phi}$ the phase precision with which any one feature
(e.g.~a dip, or the overall shape of the sinusoidal envelope) can be
tracked.  Assuming $\sigma_\phi$$\approx$$0.02$ and a 20-day baseline
over a single TESS sector yields
$\sigma_{P}$$\approx$$0.25^{+0.38}_{-0.14}$\,minutes for the
population shown in Figure~\ref{fig:evoln}; propagated forward 1{,}000
cycles yields a typical ephemeris uncertainty range of 2-11\,hours.
Measuring the period independently for each sector did not reveal
evidence for significant ($>$3$\sigma$) changes in period, implying
a period stability of $\lesssim$0.1\% over two years.

@@

The behavior during Sectors 53--58 (cycles 1233-1481) is comparatively tame; the light curve shows
only four to six dips per cycle.  Some dips remain stable in depth and
duration over this five-month interval.  Other dips grow, like the one
at $\phi = +0.06$ between cycles 1458 and 1481.  Other dips, such as
the one at $\phi = +0.12$ in cycles 1233-1264, disappear entirely.
The most dramatic state change occurs during cycle 1241, when a large
dip switches from a depth of 3\% and a duration of 3 hours to a depth
of 0.3\% and a duration of 1 hour.

@@

Examining Figure~\ref{fig:cqvs}, it is clear that CPV dips can be
asymmetric but it is not obvious whether there is a preference for
sharper ingresses or sharper egresses.  In some cases (e.g.
TIC~425933644), the flux variations do not resemble isolated dips,
making the meaning of ``ingress'' and ``egress'' unclear.  In other
cases, such as Sector~36 of TIC~89463560, there is a sharp drop with
an exponential return to the baseline flux, resembling the signatures
of exocomets \citep[e.g.][]{2018MNRAS.474.1453R,2019A&A...625L..13Z},
and the outflowing exospheres of some transiting planets
\citep[e.g.][]{2019ApJ...873...89M,2022ApJ...926..226M}.

@@

\citet{2017AJ....153..152S} previously noted a possible connection
between the CPVs and rapidly rotating magnetic B stars such as
$\sigma$~Ori~E, which can have circumstellar gas clouds trapped in
corotation \citep{2005ApJ...630L..81T}.  The $\sigma$~Ori class is
distinct from Be-star decretion disks, which are found to
systematically not host detectable magnetic fields
\citep{2013A&ARv..21...69R,2016ASPC..506..207W}.

@@

Two interesting and possibly telling exceptions to the rule that
magnetic B stars have simple light curves are HD~37776 and HD~64740.
HD~37776 is known from spectropolarimetry to have an extreme field
geometry dominated by high order multipoles
\citep{2011ApJ...726...24K}.  The field geometry of HD~64740, while
potentially less extreme, also shows evidence for a non-dipolar contribution
\citep{2018MNRAS.475.5144S}.
Recent TESS light curves
of these two B stars appear surprisingly similar to the CPV light
curves \citep{2020pase.conf...46M}.  The middle row of
Figure~\ref{fig:bstar} shows the phased TESS light curves for these
two stars, with by-eye best-matching CPVs shown underneath for
comparison.  The number of dips per cycle, the shapes of the dips, and
the dip depths relative to the sinusoidal envelope are all similar.
This connection suggests that the highly structured light curves of
both the M dwarfs and the B stars are associated with (and perhaps
caused by) strong non-dipolar magnetic fields.  Non-dipolar fields for
M dwarfs are plausible, given that Zeeman Doppler Imaging has revealed
non-axisymmetric magnetic field patterns for the few M dwarfs for
which this technique is technically feasible \citep[see][and
references therein]{2021A&ARv..29....1K}.

The physical similarity between the B stars and the M dwarfs could
have its origin in the existence of a ``centrifugal magnetosphere''
\citep[see][]{2013MNRAS.429..398P}.  In other words, both classes of
objects might satisfy the condition $R_{\rm m} > R_{\rm c}$, for
$R_{\rm m}$ the magnetosphere radius (sometimes called the Alfv\'en
radius).  Provided that charged particles are confined to move along
magnetic field lines, material can then build up at the corotation
radius \citep[see][Sec.~4, and references
therein]{2015SSRv..191..339R}.  In the converse ``dynamical'' case,
when $R_{\rm m} < R_{\rm c}$, material interior to the magnetospheric
radius returns to the stellar surface over the free-fall timescale.  A
simple estimate assuming a dipole field with $B_0\approx1\,{\rm kG}$
at the star's surface, a local plasma number density
$n\approx10^9\,{\rm cm^{-3}}$, and a plasma temperature $10^6\,{\rm
K}$ gives magnetospheric radii of order a few times the corotation
radii, $R_{\rm c}$.  This suggests that the existence of a centrifugal
magnetosphere is plausible for young, rapidly rotating M dwarfs.

@@

\vspace{-2pt}

@@

	  \setlength\itemsep{-2pt}

@@

    \item The CPV peaks and dips evolve over timescales that are both
      secular ($\approx$100\,cycles) and impulsive ($<$1 cycle).  Dip
      growth seems to happen over durations of at least ten cycles,
      and slow dip decay can also occur.  ``State-switches''
      correspond to dips collapsing instantaneously, and occur once
      every few months for both LP~12-502 and TIC~300651846.  They are
      almost always linked with observed optical flares.  Such
      switches are suggestive of magnetic reconnection opening the
      ``magnetic cage'' that traps the dust.
	\item The detailed morphology changes exhibited by LP~12-502
	during its state-switches (e.g.\ Figure~\ref{fig:lp}, cycles 1233-1264)
	imply that the flux dips are additive and independent.

@@

On the theoretical front, building a physical understanding of what sets
the characteristic size scale of the clumping material would help
clarify why the light curves have the bizarre shapes that are
observed.  The relevant puzzles in plasma physics and radiative
transfer could perhaps be connected to our understanding of the
close-in rocky planets that are expected to be present around most of
these stars.

\acknowledgments
LGB is grateful for support from the Heising-Simons 51~Pegasi~b
Fellowship, and for helpful conversations with
J.~Spake, A.~Mann, G.~Laughlin, and B.~Draine.  
We are also grateful for the assistance of S.~Yee,
L.~Weiss, H.~Isaacson, and A.~Howard in acquiring and reducing the
HIRES spectra.
This paper relied primarily on data collected by the TESS mission; the specific
2-minute cadence observations can be accessed via
DOI\,\dataset[10.17909/t9-nmc8-f686]{https://doi.org/10.17909/t9-nmc8-f686}.
Funding for the TESS mission is provided by NASA’s Science Mission
Directorate.  
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, and J.~Jenkins) and the many TESS team members for their efforts to make the mission a continued success. 
LP 12-502 in particular was observed at 2-minute
cadence thanks to the TESS Guest Investigator programs G022252 (PI:
J.~Schlieder; Sectors 18, 19, 25, 26) and G04168 (PI: R.~Jayaraman;
Sector 53). 
ADU acknowledges support by NASA under award number 80GSFC21M0002, as
well as ROSES award 22-ADAP22-0070.
